---
title: "Churn"
author: "Ronald Mego"
date: "3/1/2022"
output: html_document
---

#http://www.sthda.com/english/wiki/survival-analysis-basics

```{r}
library(tidyverse)
```

```{r}
library(survival)
```

```{r}
AIDSsurv <- tribble(
                    ~Time,~Death,
                    2    ,  1,
                    3    ,  0,
                    6    ,  1,
                    6    ,  1,
                    7    ,  1,
                    10   ,  0,
                    15   ,  1,
                    15   ,  1,
                    16   ,  1,
                    27   ,  1,
                    30   ,  1,
                    32   ,  1
                    )
```


```{r}
attach(AIDSsurv)
km.model <- survfit(Surv(Time, Death) ~1,
                     type="kaplan-meier")
```

```{r}
km.model
```

```{r}
summary(km.model)
```

```{r}
plot(km.model, conf.int = F,xlab = "Time (months)",
     ylab="%Alive = S(t)", main="KM-Model", las=1)
```

#otro ejemplo
https://www.r-bloggers.com/2017/09/survival-analysis-with-r-3/
```{r}
library(survival)
library(ranger)
library(ggplot2)
library(dplyr)
library(ggfortify)
```


```{r}
data(veteran)
head(veteran)
##   trt celltype time status karno diagtime age prior
## 1   1 squamous   72      1    60        7  69     0
## 2   1 squamous  411      1    70        5  64    10
## 3   1 squamous  228      1    60        3  38     0
## 4   1 squamous  126      1    60        9  63    10
## 5   1 squamous  118      1    70       11  65    10
## 6   1 squamous   10      1    20        5  49     0
```

```{r}
km <- with(veteran,Surv(time,status))
head(km,80)
```

```{r}
km_fit <- survfit(Surv(time,status)~1, data=veteran)
```

```{r}
summary(km_fit,times=c(1,30,60,90*(1:10)))
```

```{r}
autoplot(km_fit)
```
#otra guia
https://www.emilyzabor.com/tutorials/survival_analysis_in_r_tutorial.html
```{r}
library(survival)
library(survminer)
library(lubridate)
```


```{r}
date_ex <- tibble(
  sx_date = c("2007-06-22","2004-02-13","2010-10-27"),
  last_fup_date=c("2017-04-15","2018-07-04","2016-10-31")
)

date_ex
```

Formatting dates - lubridate package
We can also use the lubridate package to format dates. In this case, use the ymd function
```{r}
date_ex <- date_ex %>% 
  mutate(
    sx_date = ymd(sx_date), 
    last_fup_date = ymd(last_fup_date)
    )
```
Calculating survival times - lubridate
Using the lubridate package, the operator %--% designates a time interval, which is then converted to the number of elapsed seconds using as.duration and finally converted to years by dividing by dyears(1), which gives the number of seconds in a year.

```{r}
(
date_ex %>% 
  mutate(
    os_yrs = 
      as.duration(sx_date %--% last_fup_date) / dyears(1)
    )

)
```
```{r}
head(lung)
```

```{r}
bladder
```

Como completar datos

```{r}

df <- tibble(
  group = c(1:2, 1),
  item_id = c(1:2, 2),
  item_name = c("a", "b", "b"),
  value1 = 1:3,
  value2 = 4:6
)
df
```

```{r}
df %>% complete(group, nesting(item_id, item_name))
#> # A tibble: 4 × 5
#>   group item_id item_name value1 value2
#>   <dbl>   <dbl> <chr>      <int>  <int>
#> 1     1       1 a              1      4
#> 2     1       2 b              3      6
#> 3     2       1 a             NA     NA
#> 4     2       2 b              2      5
# You can also choose to fill in missing values

```


```{r}
df %>% complete(group, nesting(item_id, item_name), fill = list(value1 = 0))
#> # A tibble: 4 × 5
#>   group item_id item_name value1 value2
#>   <dbl>   <dbl> <chr>      <dbl>  <int>
#> 1     1       1 a              1      4
#> 2     1       2 b              3      6
#> 3     2       1 a              0     NA
#> 4     2       2 b              2      5
```